Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-05 inc/photocathode/plasmon/plasmon.tex
more tweaks to plasmonic section

Using the Varian e-beam deposition chamber at the UIC Nano Core Facility (NCF), I deposited a thin layer of chromium as a binding agent, then a 300nm film of gold.
This thickness of gold is several times thicker than the skin depth of green light on gold, therefore the laser radiation cannot interact with the silicon.
%TODO should I comment on the coating acting to smooth the surface to a proper sinusoid?

@@

% Content taken from 2010 ANL report
Note that for this measurement, relative emission efficiencies are calculated from the integration of the luminosity detected on the YAG scintillator screen.
The scintillator and CCD camera detection scheme was also shown to be linear (i.e., integrated signal proportional to number of electrons per pulse) for at least $10^4$ electrons per pulse, using the known linearity of single-photon photoemission from Ta irradiated by our 261nm ultraviolet laser source.
As a result, the detection scheme will accurately determine any laser power law dependence to the electron emission from the photocathode.

@@

Given the geometry of the previous measurement, notably the colinear arrangement of plasmon vector and the grating vector, the true cause is difficult to determine.
However, if instead the grating is rotated --- and the laser incidence angle is corrected to account for the longer effective periodicity of the surface --- the directionality of these effects may be separated.

@@

\ref{fig:rotated} shows the comparison of the grating vector geometries for the original scheme (top) and one in which the grating is rotated by $45^{\circ}$ (bottom).
For this rotation, the laser angle must be increased from $39^{\circ}$ to $47^{\circ}$.

The results are shown to the right in \ref{fig:rotated}.
As the divergence is clearly shown to be rotated by $45^{\circ}$ with respect to the colinear case, this experiment demonstrates that the cause of the divergence increase is due to the local field enhancements near the peaks of the grating.

This result is commensurate with the results shown by Zawadzka et al \cite{zawadzka_evanescent_2001}, who showed a reduced divergence in the Kretschmann geometry.
As that geometry does not employ a patterned surface, it would is not subject to such local field enhancements of the accelerating electric field.

@@

Although plasmonic photocathodes are still an interesting field of research in photocathode physics, we have concluded that they are not a promising candidate for an electron source for UEM at this time.
They have been difficult to manufacture and thus would be expensive for owners.
They are very intolerant to misalignment and would therefore be problematic for users.
Finally, the cannot be shown to produce the performance needed to justify the previous concerns.

>>>>

A 300nm film of gold was deposited onto the silicon using the Varian e-beam deposition chamber at the UIC Nano Core Facility (NCF); a thin layer of chromium was deposited between the silicon and gold as a binding agent.
As the gold film is several times thicker than the penetration depth of green light on gold, the laser radiation cannot interact with the silicon.
%TODO should I comment on the coating acting to smooth the surface to a proper sinusoid?

@@

% Content taken from 2010 ANL report
Note that for the following measurement, relative emission efficiencies are calculated from the integration of the luminosity detected on the YAG scintillator screen.
The scintillator and CCD camera detection scheme was also shown to be linear (i.e., integrated signal proportional to number of electrons per pulse) for at least $10^4$ electrons per pulse, using the known linearity of single-photon photoemission from Ta irradiated by our 261nm ultraviolet laser source.
As a result, the detection scheme will accurately determine any laser power law dependence to the electron emission from the photocathode.

@@

@@

Given the geometry of the previous measurement, notably the colinear arrangement of plasmon vector and the grating vector, the true cause is difficult to determine.
However, if instead the grating is rotated --- and the laser incidence angle is corrected to account for the longer effective periodicity of the surface --- the directionality of these effects may be separated.
\ref{fig:rotated} shows the comparison of the grating vector geometries for the original scheme (top) and one in which the grating is rotated by $45^{\circ}$ (bottom).
For this rotation, the laser angle must be increased from $39^{\circ}$ to $47^{\circ}$.

The results are shown to the right in \ref{fig:rotated}.
As the divergence is clearly shown to be rotated by $45^{\circ}$ with respect to the colinear case, this experiment demonstrates that the cause of the divergence increase is due to the local field enhancements near the peaks of the grating.
This result is commensurate with the results shown by Zawadzka et al \cite{zawadzka_evanescent_2001}, who showed a reduced divergence in the Kretschmann geometry.
As that geometry does not employ a patterned surface, it would is not subject to such local field enhancements of the accelerating electric field.

@@

Although plasmonic photocathodes are still an interesting field of research in photocathode physics, we have concluded that they are not a promising candidate for an electron source for UEM at this time.
They have been difficult to manufacture and thus would be expensive for owners.
They are very intolerant to misalignment and would therefore be problematic for users.
Finally, they cannot be shown to produce the performance (that is, a reduced transverse emittance) needed to justify the previous concerns.
